---
title: "project"
author: "Yixuan Li"
date: "2017???11???9???"
output: html_document
---
##**Clean up the data**
```{r,echo=FALSE}
HR_data=read.csv("HR_comma_sep.csv") 
HR_data=na.omit(HR_data)
HR_data$left=as.factor(HR_data$left)
HR_data$promotion_last_5years=as.factor(HR_data$promotion_last_5years)
summary(HR_data)
```
```{r}
library(ggplot2)
```
##**Correlation Matrix**
```{r,fig.width=12,fig.height=9}
HR_num=read.csv("HR_comma_sep.csv")
HR_num$sales=as.numeric(HR_num$sales)
HR_num$salary=as.numeric(HR_num$salary)
HR_cor=round(cor(HR_num),2)
library(reshape2)
melt_HR=melt(HR_cor)
head(melt_HR)
ggplot(melt_HR,aes(Var1,Var2,fill=value))+
  geom_tile(colour="grey50")+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 4)+
  scale_fill_distiller(palette="RdBu")+
  labs(title="Correlation Between Variables",x="",y="")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1,size = 14),axis.text.y = element_text(size = 14))
```
##**Bar plot for salary, filter by left**
```{r,fig.width=10,fig.height=2}
ggplot(HR_data,aes(left))+
  geom_bar(aes(fill=salary))+
  coord_flip()
```
##**Bar plot for working department, filter by left**
```{r,fig.width=10,fig.height=4}
ggplot(HR_data,aes(sales))+
  geom_bar(aes(fill=left),position = "dodge")+
  coord_flip()
```
##**Bar plot for salary**
```{r,fig.width=10,fig.height=2}
ggplot(HR_data,aes(salary))+
  geom_bar(aes(fill=salary))+
  coord_flip()
```
##**Bar plot for satisfaction level, with density estimate**
```{r,fig.width=6,fig.height=4}
ggplot(HR_data,aes(satisfaction_level,fill = left))+
  geom_histogram(aes(y=..density..),binwidth = 0.05,col="Black",alpha=0.5,position="identity")+
  geom_density(alpha=0.3)
```
##**Bar plot for average monthly hours, with density estimate**
```{r}
ggplot(HR_data,aes(average_montly_hours,fill = left))+
  geom_histogram(aes(y=..density..),binwidth = 10,col="Black",alpha=0.5,position="identity")+
  geom_density(alpha=0.3)
```
##**Bar plot for last evaluation, with density estimate**
```{r,fig.width=6,fig.height=4}
ggplot(HR_data,aes(last_evaluation,fill = left))+
  geom_histogram(aes(y=..density..),binwidth = 0.05,col="Black",alpha=0.5,position="identity")+
  geom_density(alpha=0.3)
```
##**Bar plot for number of projects, with density estimate**
```{r,fig.width=6,fig.height=4}
ggplot(HR_data,aes(number_project,fill = left))+
  geom_histogram(aes(y=..density..),binwidth = 1,col="Black",alpha=0.5,position="identity")+
  geom_density(alpha=0.3)
```
##**Bar plot for time spent company, with density estimate**
```{r,fig.width=6,fig.height=4}
ggplot(HR_data,aes(time_spend_company,fill = left))+
  geom_histogram(aes(y=..density..),binwidth = 1,col="Black",alpha=0.5,position="identity")+
  geom_density(alpha=0.3)
```
##**Logistic model**
```{r}
library(dplyr)
model <- glm(left ~ .,family="binomial",data=HR_data)
predicted = predict(model,newdata=HR_data,type='response')
for (i in 1:length(predicted)){
  if (predicted[i]<=0.5){
  predicted[i]=0
}else{
  predicted[i]=1
}}
table(predicted==HR_data$left)[2]/length(HR_data[,1])
```
##**Scatter plot of last evaluation and average monthly hours with regression line**
```{r}
coef_1=coef(lm(last_evaluation~average_montly_hours,data=HR_data))
ggplot(HR_data)+
  geom_jitter(aes(x=average_montly_hours,y=last_evaluation,colour=left),alpha=0.5)+
  geom_abline(intercept=coef_1[1], slope=coef_1[2], size=1)
```
##**Scatter plot of satisfaction level and average monthly hours with regression line**
```{r}
coef_2=coef(lm(satisfaction_level~average_montly_hours,data=HR_data))
ggplot(HR_data)+
  geom_jitter(aes(x=average_montly_hours,y=satisfaction_level,colour=left),alpha=0.5)+
  geom_abline(intercept=coef_2[1], slope=-coef_2[2], size=1)
```
##**Scatter plot of number of projects  and average monthly hours with regression line**
```{r}
ggplot(HR_data)+
  geom_jitter(aes(x=average_montly_hours,y=number_project,colour=left),alpha=0.5)
```

##**Decision tree model**
```{r}
library(rpart)
library(rpart.plot)
```
```{r}
HR_data = read.csv("HR_comma_sep.csv")
HR_data = na.omit(HR_data)
modified_data = HR_data %>% mutate(
  left = factor(left, labels = c("Remain", "Left")))
set.seed(1234)
test_number=sample(nrow(modified_data),size=floor(0.25*14999))
test=modified_data[test_num,]
```
```{r}
tree1=rpart(left~.,data=modified_data)
rpart.plot(tree1, type = 2, fallen.leaves = F)
result=predict(tree1,test,type="class")
real_left=gsub("0","Remain",result)
real_left=gsub("1","Left",result)
table(real_left==test$left)/floor(0.25*14999)
```
```{r}
tree2 = rpart(left ~ satisfaction_level, data = modified_data)
rpart.plot(tree2, type = 2, fallen.leaves = F, extra = 2)
result=predict(tree2,test,type="class")
real_left=gsub("0","Remain",result)
real_left=gsub("1","Left",result)
table(real_left==test$left)/floor(0.25*14999)
```
```{r}
tree3 = rpart(left ~ satisfaction_level+last_evaluation, data = modified_data)
rpart.plot(tree3, type = 2, fallen.leaves = F, extra = 2)
result=predict(tree3,test,type="class")
real_left=gsub("0","Remain",result)
real_left=gsub("1","Left",result)
table(real_left==test$left)/floor(0.25*14999)
```
```{r}
tree4 = rpart(left ~ satisfaction_level+last_evaluation+average_montly_hours, data = modified_data)
rpart.plot(tree4, type = 2, fallen.leaves = F, extra = 2)
result=predict(tree4,test,type="class")
real_left=gsub("0","Remain",result)
real_left=gsub("1","Left",result)
table(real_left==test$left)/floor(0.25*14999)
```
```{r}
tree5 = rpart(left ~ satisfaction_level+last_evaluation+average_montly_hours+number_project, data = modified_data)
rpart.plot(tree5, type = 2, fallen.leaves = F, extra = 2)
result=predict(tree5,test,type="class")
real_left=gsub("0","Remain",result)
real_left=gsub("1","Left",result)
table(real_left==test$left)/floor(0.25*14999)
```





